Parsing Postfix log files

### 2009-03-25 doc/logparser.tex
Some minor changes.
Corrections for the assumptions and database sections of the implementation chapter.
Improved Makefile to rerun latex if the list of figures or tables changes. Rearranged some parts of the rules section of the implementation chapter, and made corrections to it from proofreading.
Corrections to flowchart section of implementation chapter. Improvements to graph size so they fill the width of the page. More consistent formatting of references to the flowchart. Alphabetical ordering for the actions with the same number of rules in the action distribution graph. Added more XXX i

% Aligned list environments.
\usepackage{eqlist}

% Tell Latex to use scalable fonts
\usepackage{type1cm}
% Enable nice kerning features.
\usepackage[final]{microtype}

@@

% Sort numbers where there are multiple citations.  Does not appear to have
% the expected effect (probably clashes with varioref or hyperref), though
% it does reduce the space between numbers.
\usepackage{cite}
% Check for unused references.
% \usepackage{refcheck}

@@

%\setlength{\floatsep}{0pt}
%\setlength{\intextsep}{0pt}
%\setlength{\textfloatsep}{0pt}

% Show the citation key (e.g.\ slct-paper) in the margin beside the
% reference.
%\usepackage[nomsgs]{refcheck}
% Show where references are used.
% Neither work.
%\usepackage{citeref}
%\usepackage{backref}
%\renewcommand{\refname}{Bibliography}

% Reduce the space between items in a list; this is useful when each item
% is a single line, because then the defaul spacing makes the list look
% very sparse.  This command needs to be the first thing in a list to take
% effect.
\newcommand{\squeezeitems}[0]{%
    \setlength{\itemsep}{0pt}%
}

@@

% \showgraph{filename}{caption}{label}
\newcommand{\showgraph}[3]{%
    \begin{figure}[hbt!]
        \caption{#2}\label{#3}
        \includegraphics{#1}
    \end{figure}
}

@@

@@

\newcommand{\numberOFrules}[0]{%
    185%
}

\newcommand{\numberOFrulesMINIMUM}[0]{%
    116%
}

% \numberOFrulesMINIMUM as percentage of \numberOFrules
\newcommand{\numberOFrulesMINIMUMpercentage}[0]{%
    62.70\%%
}

% \numberOFrules as percentage increase of \numberOFrulesMINIMUM
\newcommand{\numberOFrulesMAXIMUMpercentage}[0]{%
    59.48\%%
}

@@

\newcommand{\numberOFactions}[0]{%
    18%
}

\newcommand{\numberOFruleINTERSECTIONS}[0]{%
    17,020%
}

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\acronym{PLP}}
\newcommand{\parsernames}{\acronym{PLP}'s}

@@

    \phantomsection{}
    \addcontentsline{toc}{chapter}{Abstract}

@@

XXX SHOULD I SCRAP postfix\_action?

\newpage
\tableofcontents
\listoffigures
\listoftables

>>>>

% Aligned list environments.
\usepackage{eqlist}
% This voodoo below gives us an eqlist environment with bold items.
\newcommand{\bolditem}[1]{%
    \bfseries#1%
}
\newenvironment{boldeqlist}
    {\begin{eqlist}[\renewcommand{\makelabel}{\bolditem}]}
    {\end{eqlist}}

% Enable customised lists.
\usepackage{enumitem}
% Tell Latex to use scalable fonts
\usepackage{type1cm}
% Enable nice kerning features.
\usepackage[final]{microtype}

@@

@@

% Sort numbers where there are multiple citations.  Does not appear to have
% the expected effect (probably clashes with varioref or hyperref), though
% it does reduce the space between numbers.
\usepackage{cite}
% Check for unused references, and how the citation key (e.g.\ slct-paper)
% in the margin beside the reference.
%\usepackage[nomsgs]{refcheck}
% Show where references are used; neither work.
%\usepackage{citeref}
%\usepackage{backref}
%\renewcommand{\refname}{Bibliography}

% Reduce the space between items in a list; this is useful when each item
% is a single line, because then the defaul spacing makes the list look
% very sparse.  This command needs to be the first thing in a list to take
% effect.
\newcommand{\squeezeitems}[0]{%
    \setlength{\itemsep}{0pt}%
    \setlength{\topsep}{0pt}%
    \setlength{\partopsep}{0pt}%
}

@@

% \showgraph{filename}{caption}{label}
\newcommand{\showgraph}[3]{%
    % XXX REVISIT THE PLACEMENT OF FIGURES, THOUGH I THINK LATEX'S DEFAULTS
    % AR EPROBABLY PRETTY GOOD.
    \begin{figure}%[hbt!]
        \caption{#2}\label{#3}
        \includegraphics{#1}
    \end{figure}
}

@@

\newcommand{\flowchart}[2]{%
    (action: #1\@; flowchart:~#2)%
}

@@

\newcommand{\numberOFrules}[0]{%
    184%
}

\newcommand{\numberOFrulesMINIMUM}[0]{%
    115%
}

% \numberOFrulesMINIMUM as percentage of \numberOFrules
\newcommand{\numberOFrulesMINIMUMpercentage}[0]{%
    62.50\%%
}

% \numberOFrules as percentage increase of \numberOFrulesMINIMUM
\newcommand{\numberOFrulesMAXIMUMpercentage}[0]{%
    60.00\%%
}

@@

\newcommand{\numberOFactions}[0]{%
    22%
}

\newcommand{\numberOFruleINTERSECTIONS}[0]{%
    16,836%
}

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\acronym{PLP}}
\newcommand{\parsernames}{\acronyms{PLP}}
\newcommand{\parsernamelong}{Postfix Log Parser}

@@

    \setcounter{page}{2}
    \phantomsection{}
    \addcontentsline{toc}{chapter}{Abstract}

@@

    XXX ADD A $\backslash{}$action\{\} COMMAND TO FORMAT ACTION NAMES
    CONSISTENTLY\@.

    XXX FIX THE PROBLEMS THAT AROSE FROM THE LAST all-logs RUN\@.

    XXX PLPs SHOULD BE PLP's IN A LOT OF PLACES\@; ADD A NEW COMMAND AND
    CHECK THE CURRENT USAGE\@.

    XXX SHOULD I HAVE A ``FUTURE WORK'' SECTION SOMEWHERE IN THE
    CONCLUSION\@?

\setcounter{page}{3}
\tableofcontents
\listoffigures
\listoftables
